Ae. albopictus CPP manuscript

### 2019-11-05 MS.Rmd
updated columns

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop)) + geom_point() + facet_wrap(~pop)

@@

>>>>

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK")
DI_summary$pop<-factor(DI_summary$pop, levels=c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK"))
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop)) + geom_point() + facet_wrap(~pop)

@@

### Larval collection in Japan
